\documentclass[a4paper, 14pt, oneside]{Thesis}
\usepackage{ulem}
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim} 
\usepackage{pslatex} %To set the font as Times New Roman
\usepackage{amsbsy} 
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{pdfpages}
\usepackage{epsfig}
\usepackage{verbatim} 
\usepackage{epsfig,graphics}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{subfigure}
\usepackage{tikz}
%\usepackage{fancyhdr}
%\usepackage{lipsum}
\usepackage{float}
\usepackage{url}
\usepackage{alltt}
\usepackage{longtable}
%\usepackage{mathtools}
\usepackage[boxed,ruled]{algorithm2e}[1]
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{cite}
%xs\usepackage{color}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{trees}
\graphicspath{{./images/}}
%To have 1. instead of [1] in the bibliographic entry
\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother

% To remove hyphenation
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000
%
%----To make sure the page numbers are in the top middle of each page.
\fancypagestyle{Thesis}{
\fancyhf{}
\fancyhead[C]{\thepage}
\%lfoot{\thepage}
\pagestyle{fancy}
}

\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}
%redefine the plain pagestyle
%\fancypagestyle{plain}{
%\fancyhf{}
%\fancyhead[C]{\thepage}
%}
%----------------------------------------------------------------------
%% ------------------------s----------------------------------------
\input{bmacros}
\begin{document}

\frontmatter	  % Begin Roman style (i, ii, iii, iv...) page numbering


%  Title Page

\title{\hspace*{50pt}Automatic Bug Triaging 
\newline A Machine Learning Approach}
\authors  {{ Saagarikha S.  \hspace{0.4in} 312211104086\\ \vspace{0.1in}}
{ Susindaran E.  \hspace{0.4in} 312211104111\\\vspace{0.1in}}
{ Venugopal C G.  \hspace{0.3in}312211104121\\ } }
\addresses  {\\\Computer Science \& Engineering\\\Anna University}
\date       {April 2015}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers


\Declaration{ 
%
Certified that this project report titled \textbf{``Automatic Bug Triaging A Machine Learning Approach''} is the \textit{bonafide} work of ``\textbf{Saagarikha. S (312211104086)}, \textbf{Susindaran. E (312211104111)}, and \textbf{Venugopal. C. G (312211104121)}'' who carried out the project work under my supervision. 
  \newlength{\aulength} 
  \settowidth{\aulength}{SSN College of Engineering,}
  \newlength{\auclength} 
  \settowidth{\auclength}{(HEAD OF THE DEPARTMENT)}

\begin{flushleft}
  \parbox[t]{\auclength}{\textbf{Dr. Chitra Babu}\\
    \textbf{Head of the Department}\\    
    Professor,\\
    Department of CSE,\\
    SSN College of Engineering,\\
    Kalavakkam - 603 110}
  \hfill
  \parbox[t]{\aulength}{\textbf{Dr. R. S. Milton}\\
    \textbf{Supervisor}\\
    Professor,\\
    Department of CSE,\\
    SSN College of Engineering,\\
    Kalavakkam - 603 110}
\end{flushleft}
Place:\\
Date:\\

\medskip
Submitted for the examination held on\ldots\ldots\ldots\ldots
\\
\\
\\
{\bf Internal Examiner}\hfill
{\bf External Examiner}
}
\clearpage
%% Abstract in Tamil

% Acknowledgement
%\setstretch{1.3}

\clearpage
%% ----------------------------------------------------------------

% The Abstract Page

\acknowledgements{
We thank GOD, the almighty for giving me strength and knowledge to do this project.

We would like to thank and deep sense of gratitude to my guide \textbf{Dr. R. S. Milton}, Professor, Department of Computer Science and Engineering, for his valuable advice and suggestions as well as his continued guidance, patience and support that helped me to shape and refine our work.

Our sincere thanks to  \textbf{Dr. CHITRA BABU}, Professor and Head of the Department of Computer Science and Engineering, for her words of advice and encouragement and we would like to thank our project Coordinator \textbf{Dr. S. SHEERAZUDDIN}, Professor, Department of Computer Science and Engineering for his valuable suggestions throughout this first phase of project.

We express our deep respect to the founder \textbf{Dr. SHIV NADAR}, Chairman, SSN Institutions. We also express our appreciation to our \textbf{Dr. S. SALIVAHANAN}, Principal, for all the help he has rendered during this course of study.

 We would like to extend our sincere thanks to all the teaching and non-teaching staffs of our department who have contributed directly and indirectly during the course of our project work.
Finally, we would like to thank our parents and friends for their patience, cooperation and moral support throughout our life. 
\newline
\newline
\newline
{\bf Saagarikha S.}\hfill {\bf Susindaran E.}\hfill {\bf Venugopal C G.}
}
\clearpage  % Abstract ended, start a new page

\addtotoc{ABSTRACT} % Add the "Abstract" page entry to the Contents
\abstract{ \begin{spacing}{2}
For popular software systems, the number of daily submitted bug reports is high. Triaging these incoming reports is a time consuming task. Part of the bug triage is the assignment of a report to a developer with the appropriate expertise. In this paper, we present an approach to automatically suggest developers who have the appropriate expertise for handling a bug report, based on the identified component obtained from the short description of the bug report. Our work is the first to examine the impact of multiple machine learning dimensions (classifiers and training history) along with the ranked list of developers for prediction accuracy in bug assignment. We validate our approach on Eclipse covering 2,868,000 bug reports consisting of 253 components. We demonstrate that our techniques can achieve upto 80.05\%\ prediction accuracy in bug assignment and significantly reduce the aberrant assignment of bugs. We compared the prediction time for our dataset using various algorithms such as Naive Bayes Text Classifier, Multinomial Naive Bayes and Linear SVM. We arrived at a conclusion that SVM provides higher accuracy and less learning time.
\end{spacing} 
\clearpage
%%% DUMMY PAGE FOR TAMIL ABSTRACT WHICH WILL BE PRINTED SEPARATELY
%%% Since LaTeX can't print tamil characters, you've to type tamil 
%%% abstract in some other editors and print it separately. When
%%% binding the thesis place the tamil abstract in place of this blank page
%%% I'm adding this blank page for Table of Contents to point to the right page

%\pagestyle{empty}
%\newpage
%\mbox{}
%\clearpage

\pagestyle{plain}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back

%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"

\tableofcontents % Write out the Table of Contents


%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
%\begin{spacing}{4}
%\hspace{2.5in} \textbf{List of Tables} \par 
\listoftables
%4.9 TOSSING GRAPH			. . . . . . . . . . . .  22
%\end{spacing}

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures
 %2.1 MODULE DIAGRAM			. . . . . . . . . . . .  4 \newline
%2.2 ARCHITECTURE DIAGRAM   . . . . . . . . . . . .  5 \newline
%4.8 FOLDING					. . . . . . . . . . . .  20 \newline
%7.1 EXPERIMENTAL SETUP		. . . . . . . . . . . .  28 \newline

 % Write out the List of Tables


\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{myheadings}  % Return the page headers back to the "fancy" style

\begin{spacing}{1.5}
\input{chapter1} % INTRODUCTION
\input{chapter2} % LITERATURE SURVEY
\input{chapter3} % DESIGN
\input{chapter4} % IMPLEMENTATION
\input{chapter5} % CONCLUSION AND FUTURE WORK
\input{chapter6}
\input{chapter7} % Result
%\input{Bibliography} 

\end{spacing}
\newpage
\appendix
%\input{chapter8}
%\input{chapter8}
%\addtotoc{REFERENCES}
%\cite{Akers78}
%\bibliographystyle{plain}

%\bibliography{ref}


\begin{thebibliography}{99}
 \bibliographystyle{plain}

\bibitem[1]{icse} Anvik, J., Hiew, L., G. C. Murphy (2006), `Who should fix this bug $?$', In proc. of ICSE`06, 
pp. 361-370.

\bibitem[2]{ucr} Bhattacharyaa, P., Neamtiua, I. (2010), `Automated, Highly-Accurate, Bug Assignment Using Machine Learning and Tossing Graphs',  In proc. of ICSM`10, pp.1-10.

\bibitem[3]{seke} Cubranic, D., Murphy, G.C., (2004), `Automatic bug triage using text categorization', In proc. of SEKE`04 .

\bibitem[4]{fse} Jeong, G., Kim, S., Zimmermann, T.,  (2009), `Improving Bug Triage with Bug Tossing Graphs', In proc. of FSE`09.

\bibitem[5]{esem} Lin, Z., Shu, F., Yang,Y., Hu,C., Wang, Q., (2009), `An empirical study on bug
assignment automation using Chinese bug data', In proc. of ESEM`09.

\bibitem[6]{dataset} The Eclipse and Mozilla Defect Tracking Dataset(2013)\newline Available From: $<https://github.com/ansymo/msr2013-bug\_dataset>$.

\end{thebibliography}


\end{document} 
